paper2_resistance_mechanisms_mixtures

### 2016-06-15 inst/documents/paper1_results_figs_rr.Rmd
to 0.5

  #remove runs that didn't reach a resistance threshold (999), even if just for one strategy
  #>1000 excludes sequential strategy that had a 999 in
  #BEWARE would need to increase 1000 if I increase max generations in the runs
  didntReachThresh <- which( dif_mixA_seq$gen_cP0.25 > 500 | dif_mixA_seq$gen_cP0.25seq > 500 )
  #subset by runs not making threshold
  dif_mixA_seq <- dif_mixA_seq[-didntReachThresh,]

  dif_mixA_seq["mixA_minus_seq0.25"] <- dif_mixA_seq["gen_cP0.25"] - dif_mixA_seq["gen_cP0.25seq"]

  #for dif_mix2_seq
  didntReachThresh <- which( dif_mix2_seq$gen_cP0.25 > 500 | dif_mix2_seq$gen_cP0.25seq > 500 )
  #subset by runs not making threshold
  dif_mix2_seq <- dif_mix2_seq[-didntReachThresh,]

  dif_mix2_seq["mix2_minus_seq0.25"] <- dif_mix2_seq["gen_cP0.25"] - dif_mix2_seq["gen_cP0.25seq"]

@@

    y <- "mixA_minus_seq0.25"

@@

  #can I do a 2D hexbin plot with x=exposure, y=effectiveness
  #but do I just want to use 1 effectiveness, or maybe add both effectivenesses together ?
  #bin colour : proportion of runs in which sequential better & could have diverging scale about 0.5
  #I probably still need to tweak data first
  #currently I have differences in times to resistance : mixA_minus_seq0.25
  #what I think I want is the proportion of runs in which mix is better
  #I can get that by setting to 0 & 1 and calc average
  # tst_runs <- c(1,0,0,0)
  # tst_runs <- c(1,1,1,0)
  # mean(tst_runs)

@@

  #if mix-seq >1 resistance took longer for mix so mix is better
  ggSubset$mixA_better_seq0.25 <- ifelse( ggSubset$mixA_minus_seq0.25 > 0, 1, 0 )
  ggSubset$seq_better_mixA0.25 <- ifelse( ggSubset$mixA_minus_seq0.25 < 0, 1, 0 )
  ggSubset$abs_mixA_minus_seq0.25 <- abs(ggSubset$mixA_minus_seq0.25)

  #tricky
  #be a bit careful what to do with zeros where results are same for both strategies
  #I use these better vars to facet the plots
  #may want the zeroes in both facets
  #to get that I can rbind the zeros from one onto the other BEWARE this may screw up existing plots
  df_same <- ggSubset[which(ggSubset$mixA_minus_seq0.25==0),]
  #set these to 1 (they were 0)
  df_same$mixA_better_seq0.25 <- 1
  df_same$seq_better_mixA0.25 <- 1
  #rbind them back onto other dataset, probably not needed ??
  ggSubset <- rbind( ggSubset, df_same)

  #add an option for 20% better, put the not in to get facets in correct order in ggplot later
  ggSubset$mixA_not20pc_better_seq0.25 <- ifelse( ggSubset$mixA_minus_seq0.25 / ggSubset$gen_cP0.25seq <= 0.2, 1, 0 )

    #failed hex plot just gave me counts
    # print( ggplot(ggSubset, aes_string(x='exposure', y='effectiveness_insecticide1', colour='mixA_better_seq0.25'))+
    #          geom_hex()
    #        )

    #interesting plot showing where sequence is better is restricted to higher values of exposure and effectiveness 
    print( ggplot(ggSubset, aes_string(x='exposure', y='effectiveness_insecticide1', colour='mixA_better_seq0.25'))+
             #geom_hex()
             geom_point(alpha=0.2)  
           )

    #can I multiply the two effectivenesses together ?
    #aha! yes that's even better
    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 * effectiveness_insecticide2, colour=mixA_better_seq0.25))+
             #geom_hex()
             geom_point(alpha=0.2)  
           )

    #i think adding the effectivenesses may give an even better plot
    #and makes it easier for the reader to interpret
    #aha! yes that's even better
    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2, colour=mixA_better_seq0.25))+

@@

    #facetted 0/1, labelled mix better, seq better
    #if I get this sorted I could try to have +ve & -ve on the same scale
    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2, colour=seq_better_mixA0.25))+
             facet_grid( ~ seq_better_mixA0.25, labeller=as_labeller( c('0'='adaptive mix better','1'='sequential better'))) +

@@

    #what if I do the difference rather than just 0/1
    #aha! this is close to being the killer plot, just need to get the colour scale right 
    #but the previous one may be clearer
    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 * effectiveness_insecticide2, colour=mixA_minus_seq0.25))+
             #geom_hex()
             geom_point(alpha=1) +
             #no adding grey outlines obscures the pattern
             #geom_point(shape=21, colour='grey') +
             #this one does look good but slight potential to see negatives above even though they aren't there
             #could I modify the shapes to be different
             #would a repeated, faceted plot solve that ?
             #scale looks good but colours could do with being denser
             #and I'm not sure that making the points that are close to zero white is a good idea ?
             #although it does mean points that are only a few generations different do not obscure the pattern
             #maybe I could explicitly do Ians 20% thing & colour those white
             scale_colour_gradient2()

@@

    #COOLIO !! I really like this figure.
    library(viridis)
    #facet showing generation differences, labelled mix better, seq better
    #+ve & -ve on the same colour scale
    #failed attempt at getting Curtis point in legend
    #print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2, colour=abs_mixA_minus_seq0.25, size="Curtis"))+
    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2, colour=abs_mixA_minus_seq0.25))+

             facet_grid( ~ seq_better_mixA0.25, labeller=as_labeller( c('0'='adaptive mix better','1'='sequential better'))) +

@@

    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2, colour=abs_mixA_minus_seq0.25))+

             facet_grid( ~ seq_better_mixA0.25, labeller=as_labeller( c('0'='adaptive mix better','1'='sequential better'))) +

             scale_color_viridis(begin=1, end=0, option="viridis", 
                                 guide=guide_colourbar(title="difference in \ngenerations to reach\nresistance threshold")) + 
             theme_bw() +
             #add point for Curtis inputs
             geom_point(data = curtisInputs, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2), colour='red', shape=3) +
             ylab('effectiveness of insecticides added') +
             xlab('exposure to both insecticides') + 
             #main points for the plot
             geom_point(alpha=1, size=0.5) + 
             #!!!NOW can I add a lm fitted to the 0 points mixA_minus_seq0.25
             geom_smooth(data=ggSubset[which(ggSubset$mixA_minus_seq0.25==0),], method = "lm", se = FALSE) +
             #can I subtley highlight the zero points which are repeated in each plot ?
             geom_point(data=ggSubset[which(ggSubset$mixA_minus_seq0.25==0),], size=0.8, colour='lightgrey', shape=2, fill='white') +            
             #add text for Curtis point
             geom_text(data = curtisInputs, inherit.aes = FALSE, aes_string(x = 'exposure', y='effectiveness_insecticide1 + effectiveness_insecticide2', label='"Curtis Fig.2"'), nudge_x=-0.05, size=3, colour='red')
           )

  # doing the lm outside of ggplot    
  df_same = ggSubset[which(ggSubset$mixA_minus_seq0.25==0),]
  x1=df_same$exposure 
  y1=df_same$effectiveness_insecticide1 + df_same$effectiveness_insecticide2

@@

  #modify the killer plot to show where mixtures are 20% better ?
  print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2))+ #, colour=abs_mixA_minus_seq0.25))+

             facet_grid( ~ mixA_not20pc_better_seq0.25, labeller=as_labeller( c('0'='adaptive mix\nresistance >20% slower','1'='adaptive mix\nresistance <20% slower'))) +

@@

  #if mix-seq >1 resistance took longer for mix so mix is better
  ggSubset$mix2_better_seq0.25 <- ifelse( ggSubset$mix2_minus_seq0.25 > 0, 1, 0 )
  ggSubset$seq_better_mix20.25 <- ifelse( ggSubset$mix2_minus_seq0.25 < 0, 1, 0 )
  ggSubset$abs_mix2_minus_seq0.25 <- abs(ggSubset$mix2_minus_seq0.25)

  #tricky
  #be a bit careful what to do with zeros where results are same for both strategies
  #I use these better vars to facet the plots
  #may want the zeroes in both facets
  #to get that I can rbind the zeros from one onto the other BEWARE this may screw up existing plots
  df_same <- ggSubset[which(ggSubset$mix2_minus_seq0.25==0),]
  #set these to 1 (they were 0)
  df_same$mix2_better_seq0.25 <- 1
  df_same$seq_better_mix20.25 <- 1
  #rbind them back onto other dataset, probably not needed ??
  ggSubset <- rbind( ggSubset, df_same)

  #add an option for 20% better, put the not in to get facets in correct order in ggplot later
  ggSubset$mix2_not20pc_better_seq0.25 <- ifelse( ggSubset$mix2_minus_seq0.25 / ggSubset$gen_cP0.25seq <= 0.2, 1, 0 )

    #i think adding the effectivenesses may give an even better plot
    #and makes it easier for the reader to interpret
    #aha! yes that's even better
    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2, colour=mix2_better_seq0.25))+

@@

    #facetted 0/1, labelled mix better, seq better
    #if I get this sorted I could try to have +ve & -ve on the same scale
    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2, colour=seq_better_mix20.25))+
             facet_grid( ~ seq_better_mix20.25, labeller=as_labeller( c('0'='mix better','1'='sequential better'))) +

@@

    #killer plot mix2 vs seq
    library(viridis)
    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2, colour=abs_mix2_minus_seq0.25))+

             facet_grid( ~ seq_better_mix20.25, labeller=as_labeller( c('0'='mix better','1'='sequential better'))) +

@@

    #modify killer plot mix2 vs seq to add in male exposure prop on x axis
    library(viridis)
    print( ggplot(ggSubset, aes(x=exposure+exposure*maleExposureProp, y=effectiveness_insecticide1 + effectiveness_insecticide2, colour=abs_mix2_minus_seq0.25))+

             facet_grid( ~ seq_better_mix20.25, labeller=as_labeller( c('0'='mix better','1'='sequential better'))) +
             scale_color_viridis(begin=1, end=0, option="viridis", 
                                 guide=guide_colourbar(title="difference in \ngenerations to reach\nresistance threshold")) + 
             theme_bw() +
             #add point for Curtis inputs
             geom_point(data = curtisInputs, aes(x=exposure+exposure*maleExposureProp, y=effectiveness_insecticide1 + effectiveness_insecticide2), colour='red', shape=3) +
             ylab('effectiveness of insecticides added') +
             xlab('exposure to both insecticides for both sexes') + 
             #main points for the plot
             geom_point(alpha=1, size=0.5) + 
             #add text for Curtis point
             geom_text(data = curtisInputs, inherit.aes = FALSE, aes_string(x = 'exposure', y='effectiveness_insecticide1 + effectiveness_insecticide2', label='"Curtis Fig.2"'), nudge_x=-0.05, size=3, colour='red')
           )

  #modify the killer plot to show where mixtures are 20% better ?
  print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2))+ #, colour=abs_mixA_minus_seq0.25))+

             facet_grid( ~ mix2_not20pc_better_seq0.25, labeller=as_labeller( c('0'='mix\nresistance >20% slower','1'='mix\nresistance <20% slower'))) +

@@

    print( ggplot( to_plot, aes_string(x='inputs',y='PRCC') ) + 
             geom_point(shape=1, colour='red') +
             theme(axis.text.x = element_text(angle = 45,hjust = 1, vjust = 1)) +
             geom_hline(yintercept = 0, linetype=3) +
             ylim(-1,1) +
             #ggtitle(paste(strategy,"PRCC")) +
             ggtitle(paste(strategy,"time-to-resistance 0.25")) +
             xlab(NULL)
          )
  }

@@

    y <- 'time_to_resistance0.25'    
    #y <- 'time_to_resistance0.5'
    color <- 'strategy'
    #coloring by exposure shows its effect even when other params are varying
    #color <- 'exposure'

>>>>

  #remove runs that didn't reach a resistance threshold (999), even if just for one strategy
  #>1000 excludes sequential strategy that had a 999 in
  #BEWARE would need to increase 1000 if I increase max generations in the runs
  didntReachThresh <- which( dif_mixA_seq$gen_cP0.5 > 500 | dif_mixA_seq$gen_cP0.5seq > 500 )
  #subset by runs not making threshold
  dif_mixA_seq <- dif_mixA_seq[-didntReachThresh,]

  dif_mixA_seq["mixA_minus_seq0.5"] <- dif_mixA_seq["gen_cP0.5"] - dif_mixA_seq["gen_cP0.5seq"]

  #for dif_mix2_seq
  didntReachThresh <- which( dif_mix2_seq$gen_cP0.5 > 500 | dif_mix2_seq$gen_cP0.5seq > 500 )
  #subset by runs not making threshold
  dif_mix2_seq <- dif_mix2_seq[-didntReachThresh,]

  dif_mix2_seq["mix2_minus_seq0.5"] <- dif_mix2_seq["gen_cP0.5"] - dif_mix2_seq["gen_cP0.5seq"]

@@

    y <- "mixA_minus_seq0.5"

@@

  #can I do a 2D hexbin plot with x=exposure, y=effectiveness
  #but do I just want to use 1 effectiveness, or maybe add both effectivenesses together ?
  #bin colour : proportion of runs in which sequential better & could have diverging scale about 0.5
  #I probably still need to tweak data first
  #currently I have differences in times to resistance : mixA_minus_seq0.5
  #what I think I want is the proportion of runs in which mix is better
  #I can get that by setting to 0 & 1 and calc average
  # tst_runs <- c(1,0,0,0)
  # tst_runs <- c(1,1,1,0)
  # mean(tst_runs)

@@

  #if mix-seq >1 resistance took longer for mix so mix is better
  ggSubset$mixA_better_seq0.5 <- ifelse( ggSubset$mixA_minus_seq0.5 > 0, 1, 0 )
  ggSubset$seq_better_mixA0.5 <- ifelse( ggSubset$mixA_minus_seq0.5 < 0, 1, 0 )
  ggSubset$abs_mixA_minus_seq0.5 <- abs(ggSubset$mixA_minus_seq0.5)

  #tricky
  #be a bit careful what to do with zeros where results are same for both strategies
  #I use these better vars to facet the plots
  #may want the zeroes in both facets
  #to get that I can rbind the zeros from one onto the other BEWARE this may screw up existing plots
  df_same <- ggSubset[which(ggSubset$mixA_minus_seq0.5==0),]
  #set these to 1 (they were 0)
  df_same$mixA_better_seq0.5 <- 1
  df_same$seq_better_mixA0.5 <- 1
  #rbind them back onto other dataset, probably not needed ??
  ggSubset <- rbind( ggSubset, df_same)

  #add an option for 20% better, put the not in to get facets in correct order in ggplot later
  ggSubset$mixA_not20pc_better_seq0.5 <- ifelse( ggSubset$mixA_minus_seq0.5 / ggSubset$gen_cP0.5seq <= 0.2, 1, 0 )

    #failed hex plot just gave me counts
    # print( ggplot(ggSubset, aes_string(x='exposure', y='effectiveness_insecticide1', colour='mixA_better_seq0.5'))+
    #          geom_hex()
    #        )

    #interesting plot showing where sequence is better is restricted to higher values of exposure and effectiveness 
    print( ggplot(ggSubset, aes_string(x='exposure', y='effectiveness_insecticide1', colour='mixA_better_seq0.5'))+
             #geom_hex()
             geom_point(alpha=0.2)  
           )

    #can I multiply the two effectivenesses together ?
    #aha! yes that's even better
    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 * effectiveness_insecticide2, colour=mixA_better_seq0.5))+
             #geom_hex()
             geom_point(alpha=0.2)  
           )

    #i think adding the effectivenesses may give an even better plot
    #and makes it easier for the reader to interpret
    #aha! yes that's even better
    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2, colour=mixA_better_seq0.5))+

@@

    #facetted 0/1, labelled mix better, seq better
    #if I get this sorted I could try to have +ve & -ve on the same scale
    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2, colour=seq_better_mixA0.5))+
             facet_grid( ~ seq_better_mixA0.5, labeller=as_labeller( c('0'='adaptive mix better','1'='sequential better'))) +

@@

    #what if I do the difference rather than just 0/1
    #aha! this is close to being the killer plot, just need to get the colour scale right 
    #but the previous one may be clearer
    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 * effectiveness_insecticide2, colour=mixA_minus_seq0.5))+
             #geom_hex()
             geom_point(alpha=1) +
             #no adding grey outlines obscures the pattern
             #geom_point(shape=21, colour='grey') +
             #this one does look good but slight potential to see negatives above even though they aren't there
             #could I modify the shapes to be different
             #would a repeated, faceted plot solve that ?
             #scale looks good but colours could do with being denser
             #and I'm not sure that making the points that are close to zero white is a good idea ?
             #although it does mean points that are only a few generations different do not obscure the pattern
             #maybe I could explicitly do Ians 20% thing & colour those white
             scale_colour_gradient2()

@@

    #COOLIO !! I really like this figure.
    library(viridis)
    #facet showing generation differences, labelled mix better, seq better
    #+ve & -ve on the same colour scale
    #failed attempt at getting Curtis point in legend
    #print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2, colour=abs_mixA_minus_seq0.5, size="Curtis"))+
    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2, colour=abs_mixA_minus_seq0.5))+

             facet_grid( ~ seq_better_mixA0.5, labeller=as_labeller( c('0'='adaptive mix better','1'='sequential better'))) +

@@

    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2, colour=abs_mixA_minus_seq0.5))+

             facet_grid( ~ seq_better_mixA0.5, labeller=as_labeller( c('0'='adaptive mix better','1'='sequential better'))) +

             scale_color_viridis(begin=1, end=0, option="viridis", 
                                 guide=guide_colourbar(title="difference in \ngenerations to reach\nresistance threshold")) + 
             theme_bw() +
             #add point for Curtis inputs
             geom_point(data = curtisInputs, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2), colour='red', shape=3) +
             ylab('effectiveness of insecticides added') +
             xlab('exposure to both insecticides') + 
             #main points for the plot
             geom_point(alpha=1, size=0.5) + 
             #!!!NOW can I add a lm fitted to the 0 points mixA_minus_seq0.5
             geom_smooth(data=ggSubset[which(ggSubset$mixA_minus_seq0.5==0),], method = "lm", se = FALSE) +
             #can I subtley highlight the zero points which are repeated in each plot ?
             geom_point(data=ggSubset[which(ggSubset$mixA_minus_seq0.5==0),], size=0.8, colour='lightgrey', shape=2, fill='white') +            
             #add text for Curtis point
             geom_text(data = curtisInputs, inherit.aes = FALSE, aes_string(x = 'exposure', y='effectiveness_insecticide1 + effectiveness_insecticide2', label='"Curtis Fig.2"'), nudge_x=-0.05, size=3, colour='red')
           )

  # doing the lm outside of ggplot    
  df_same = ggSubset[which(ggSubset$mixA_minus_seq0.5==0),]
  x1=df_same$exposure 
  y1=df_same$effectiveness_insecticide1 + df_same$effectiveness_insecticide2

@@

  #modify the killer plot to show where mixtures are 20% better ?
  print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2))+ #, colour=abs_mixA_minus_seq0.5))+

             facet_grid( ~ mixA_not20pc_better_seq0.5, labeller=as_labeller( c('0'='adaptive mix\nresistance >20% slower','1'='adaptive mix\nresistance <20% slower'))) +

@@

  #if mix-seq >1 resistance took longer for mix so mix is better
  ggSubset$mix2_better_seq0.5 <- ifelse( ggSubset$mix2_minus_seq0.5 > 0, 1, 0 )
  ggSubset$seq_better_mix20.5 <- ifelse( ggSubset$mix2_minus_seq0.5 < 0, 1, 0 )
  ggSubset$abs_mix2_minus_seq0.5 <- abs(ggSubset$mix2_minus_seq0.5)

  #tricky
  #be a bit careful what to do with zeros where results are same for both strategies
  #I use these better vars to facet the plots
  #may want the zeroes in both facets
  #to get that I can rbind the zeros from one onto the other BEWARE this may screw up existing plots
  df_same <- ggSubset[which(ggSubset$mix2_minus_seq0.5==0),]
  #set these to 1 (they were 0)
  df_same$mix2_better_seq0.5 <- 1
  df_same$seq_better_mix20.5 <- 1
  #rbind them back onto other dataset, probably not needed ??
  ggSubset <- rbind( ggSubset, df_same)

  #add an option for 20% better, put the not in to get facets in correct order in ggplot later
  ggSubset$mix2_not20pc_better_seq0.5 <- ifelse( ggSubset$mix2_minus_seq0.5 / ggSubset$gen_cP0.5seq <= 0.2, 1, 0 )

    #i think adding the effectivenesses may give an even better plot
    #and makes it easier for the reader to interpret
    #aha! yes that's even better
    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2, colour=mix2_better_seq0.5))+

@@

    #facetted 0/1, labelled mix better, seq better
    #if I get this sorted I could try to have +ve & -ve on the same scale
    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2, colour=seq_better_mix20.5))+
             facet_grid( ~ seq_better_mix20.5, labeller=as_labeller( c('0'='mix better','1'='sequential better'))) +

@@

    #killer plot mix2 vs seq
    library(viridis)
    print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2, colour=abs_mix2_minus_seq0.5))+

             facet_grid( ~ seq_better_mix20.5, labeller=as_labeller( c('0'='mix better','1'='sequential better'))) +

@@

    #modify killer plot mix2 vs seq to add in male exposure prop on x axis
    library(viridis)
    print( ggplot(ggSubset, aes(x=exposure+exposure*maleExposureProp, y=effectiveness_insecticide1 + effectiveness_insecticide2, colour=abs_mix2_minus_seq0.5))+

             facet_grid( ~ seq_better_mix20.5, labeller=as_labeller( c('0'='mix better','1'='sequential better'))) +
             scale_color_viridis(begin=1, end=0, option="viridis", 
                                 guide=guide_colourbar(title="difference in \ngenerations to reach\nresistance threshold")) + 
             theme_bw() +
             #add point for Curtis inputs
             geom_point(data = curtisInputs, aes(x=exposure+exposure*maleExposureProp, y=effectiveness_insecticide1 + effectiveness_insecticide2), colour='red', shape=3) +
             ylab('effectiveness of insecticides added') +
             xlab('exposure to both insecticides for both sexes') + 
             #main points for the plot
             geom_point(alpha=1, size=0.5) + 
             #add text for Curtis point
             geom_text(data = curtisInputs, inherit.aes = FALSE, aes_string(x = 'exposure', y='effectiveness_insecticide1 + effectiveness_insecticide2', label='"Curtis Fig.2"'), nudge_x=-0.05, size=3, colour='red')
           )

  #modify the killer plot to show where mixtures are 20% better ?
  print( ggplot(ggSubset, aes(x=exposure, y=effectiveness_insecticide1 + effectiveness_insecticide2))+ #, colour=abs_mixA_minus_seq0.5))+

             facet_grid( ~ mix2_not20pc_better_seq0.5, labeller=as_labeller( c('0'='mix\nresistance >20% slower','1'='mix\nresistance <20% slower'))) +

@@

    print( ggplot( to_plot, aes_string(x='inputs',y='PRCC') ) + 
             geom_point(shape=1, colour='red') +
             theme(axis.text.x = element_text(angle = 45,hjust = 1, vjust = 1)) +
             geom_hline(yintercept = 0, linetype=3) +
             ylim(-1,1) +
             #ggtitle(paste(strategy,"PRCC")) +
             ggtitle(paste(strategy,"time-to-resistance 0.5")) +
             xlab(NULL)
          )
  }

@@

    y <- 'time_to_resistance0.5'    
    #y <- 'time_to_resistance0.5'
    color <- 'strategy'
    #coloring by exposure shows its effect even when other params are varying
    #color <- 'exposure'
